\documentclass[11pt, a4paper]{article}

% =========================================================
% PACKAGES
% =========================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{booktabs} % For professional tables
\usepackage{array}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{helvet} % Modern Sans-Serif font
\usepackage{setspace}

% =========================================================
% CONFIGURATION
% =========================================================

% Set Margins
\geometry{top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm}

% Set Font to Helvetica (Arial-like)
\renewcommand{\familydefault}{\sfdefault}

% Spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}
\onehalfspacing

% Colors
\definecolor{BrandBlue}{RGB}{0, 51, 102}
\definecolor{BrandRed}{RGB}{153, 0, 0}
\definecolor{SectionGrey}{RGB}{60, 60, 60}

% Hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=BrandBlue,
    urlcolor=BrandBlue,
    pdfborder={0 0 0}
}

% Headers and Footers
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Ignition AI}}
\rhead{Master Business Plan v3.0}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Section Styling
\titleformat{\section}
{\color{BrandBlue}\Large\bfseries\uppercase}
{\thesection}{1em}{}

\titleformat{\subsection}
{\color{SectionGrey}\large\bfseries}
{\thesubsection}{1em}{}

% Table Styling
\renewcommand{\arraystretch}{1.4}

% =========================================================
% DOCUMENT START
% =========================================================
\begin{document}

% ---------------------------------------------------------
% TITLE PAGE
% ---------------------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{3cm}

    {\Huge \textbf{IGNITION AI} \par}
    \vspace{0.5cm}
    {\Large \textit{The Operating System for Edge Intelligence \& Security} \par}

    \vspace{1.5cm}
    \rule{\linewidth}{0.5mm}
    \vspace{1.5cm}

    {\Huge \textbf{MASTER BUSINESS PLAN} \par}
    \vspace{0.5cm}
    {\Large Version 3.0 (Enterprise \& Hardware Agnostic) \par}
    \vspace{0.5cm}
    {\large \today \par}

    \vspace{4cm}

    \textbf{Sector:} Cybersecurity / Edge AI / Deep Tech \\
    \textbf{Funding Stage:} Pre-Seed / Seed \\
    \textbf{Product:} Blackbox Platform \\

    \vfill

    \textbf{Contact:} \\
    Founder \& CEO \\
    [Email Address] \\
    [Phone Number] \\
    ignition-ai.com

    \vspace{1cm}
    {\footnotesize \textbf{CONFIDENTIAL} \\ This document contains proprietary information.}
\end{titlepage}

% ---------------------------------------------------------
% EXECUTIVE SUMMARY
% ---------------------------------------------------------
\section{Executive Summary}

\textbf{Ignition AI} is an infrastructure software company building the world’s first hardware-agnostic, real-time AI security platform. Our flagship product, \textbf{Blackbox}, decouples high-performance AI from expensive hardware, allowing enterprises to run military-grade threat detection on existing infrastructure—from multi-million dollar data centers to \$50 industrial gateways.

Current cybersecurity solutions (SIEM/XDR) are trapped in a ``Cloud-Only'' or ``NVIDIA-Only'' paradigm. This forces customers to transport petabytes of sensitive data to the cloud (latency/cost) or purchase specialized hardware (CapEx).

Ignition AI solves this via \textbf{\texttt{xInfer}}, our proprietary inference engine that dynamically recompiles AI models to run on \textit{any} available silicon (Intel CPUs, AMD APUs, Rockchip NPUs, or NVIDIA GPUs) with near-zero overhead. By bringing intelligence to the data, rather than data to the intelligence, we reduce infrastructure costs by 90\% and detection latency from minutes to microseconds.

\textbf{The Ask:} We are raising \textbf{\$1.5M} to finalize the \texttt{xInfer} hardware matrix, launch the Enterprise Edition of Blackbox, and secure our first 10 strategic industrial partnerships.

% ---------------------------------------------------------
% COMPANY OVERVIEW
% ---------------------------------------------------------
\section{Company Overview}

\subsection{Mission}
To secure the autonomous world by making AI detection ubiquitous, instant, and accessible on any device, anywhere.

\subsection{Vision}
A future where every router, server, and factory controller has a ``Blackbox'' running inside it—a self-contained, self-healing immune system that requires no cloud connectivity to stop threats.

\subsection{The ``Why Now?''}
Three macro-trends have converged to create the perfect storm for Ignition AI:
\begin{enumerate}
    \item \textbf{The Edge Compute Explosion:} By 2027, 75\% of enterprise data will be created at the edge (Gartner). Current security tools cannot run there.
    \item \textbf{The Silicon Renaissance:} Every chip manufacturer (Intel, AMD, Apple) is adding ``NPU'' (Neural Processing) cores to consumer chips. Software is lagging behind hardware. Blackbox bridges this gap.
    \item \textbf{Data Sovereignty:} GDPR and Defense regulations are making it harder to ship logs to the cloud. Local processing is no longer a luxury; it is a legal necessity.
\end{enumerate}

% ---------------------------------------------------------
% MARKET ANALYSIS
% ---------------------------------------------------------
\section{Market Analysis}

\subsection{Total Addressable Market (TAM)}
\begin{itemize}
    \item \textbf{Next-Gen SIEM \& XDR (\$22B):} Enterprises drowning in Splunk bills ($>$ \$1M/year) need a way to filter noise at the source.
    \item \textbf{Industrial IoT Security (\$38B):} Factories run on legacy hardware that cannot support heavy Python/Java agents. Our C++ agent is the solution.
    \item \textbf{Edge AI Infrastructure (\$59B):} We license the \texttt{xInfer} runtime as a standalone engine to non-security companies (e.g., Drones, Retail).
\end{itemize}

\subsection{Competitive Landscape}
\begin{table}[h]
    \centering
    \begin{tabular}{@{}p{3cm} p{3cm} p{3cm} p{3cm}@{}}
        \toprule
        \textbf{Competitor} & \textbf{Architecture} & \textbf{Latency} & \textbf{Hardware Req} \\
        \midrule
        \textbf{Splunk} & Java / Batch & Minutes & Heavy Servers \\
        \textbf{CrowdStrike} & Cloud-Native & Seconds & Cloud Only \\
        \textbf{Darktrace} & Appliance & Milliseconds & Proprietary HW \\
        \textbf{Blackbox} & \textbf{Edge C++} & \textbf{$<$1ms} & \textbf{Any Silicon} \\
        \bottomrule
    \end{tabular}
\end{table}

% ---------------------------------------------------------
% PRODUCT & TECHNOLOGY
% ---------------------------------------------------------
\section{Product \& Technology}

Our platform consists of the \textbf{Blackbox Ecosystem}, powered by the \textbf{xInfer Core}.

\subsection{The Core Differentiator: xInfer}
A C++20 Hardware Abstraction Layer (HAL) that unifies AI execution. Instead of writing code for one chip, our engine dynamically adapts to the available hardware at runtime.

\begin{itemize}
    \item \textbf{NVIDIA (TensorRT):} Uses massive parallelism for Data Centers (100k+ EPS).
    \item \textbf{Intel / AMD (OpenVINO):} Leverages AVX-512 and iGPUs on standard servers.
    \item \textbf{Rockchip / NXP (NPU):} Utilizes dedicated accelerators on Industrial Gateways.
\end{itemize}

\subsection{The Blackbox Suite}
\begin{enumerate}
    \item \textbf{Blackbox Core:} The engine. Processes 100k+ EPS on commodity CPUs via Zero-Copy ingestion.
    \item \textbf{Sentry Micro:} IoT Agent written in C99. Runs on routers/PLCs using $<50$MB RAM.
    \item \textbf{Tower:} Centralized fleet control plane for managing 100,000+ nodes.
    \item \textbf{Matrix:} Built-in ``Cyber Range'' simulator to stress-test defenses.
    \item \textbf{Sim:} R\&D lab that trains models and exports them to universal ONNX artifacts.
\end{enumerate}

% ---------------------------------------------------------
% BUSINESS MODEL
% ---------------------------------------------------------
\section{Business Model}

We utilize an \textbf{Open Core} model to drive adoption, with Enterprise Features driving revenue.

\subsection{Revenue Streams}
\begin{itemize}
    \item \textbf{Enterprise Licensing (Recurring):} Per-node subscription.
    \begin{itemize}
        \item Server Node: \$10/month.
        \item IoT Node: \$0.50/month (Volume based).
    \end{itemize}
    \item \textbf{OEM Partnerships (Royalty):} Hardware manufacturers (Cisco, Siemens) pre-install \texttt{sentry-micro} on their devices. We take a royalty fee per device sold.
    \item \textbf{``The Foundry'' (Professional Services):} We train bespoke AI models for industrial clients with unique machinery vibration patterns.
\end{itemize}

% ---------------------------------------------------------
% GTM STRATEGY
% ---------------------------------------------------------
\section{Go-to-Market Strategy}

\begin{itemize}
    \item \textbf{Phase 1: Developer Love (Months 1-6):} Publish benchmarks comparing Blackbox vs. Logstash. Release ``The Matrix'' simulator as open-source. Goal: 5,000 GitHub Stars.
    \item \textbf{Phase 2: The ``Trojan Horse'' (Months 6-12):} Target DevOps engineers. Offer a free ``Log Reducer'' utility to lower their Splunk bills by 50\%.
    \item \textbf{Phase 3: Strategic OEM (Year 2):} Approach chipset vendors (Intel, AMD). Show them that Blackbox makes their chips look powerful. Leverage their sales channels.
\end{itemize}

% ---------------------------------------------------------
% ROADMAP
% ---------------------------------------------------------
\section{Operational Roadmap}

\begin{table}[h]
    \centering
    \begin{tabular}{@{}p{2.5cm} p{11cm}@{}}
        \toprule
        \textbf{Timeline} & \textbf{Key Deliverables} \\
        \midrule
        \textbf{Q1 2026} & \textbf{Product Hardening:} Complete Unit Tests. Finish Vacuum connectors (AWS/Azure). Release v0.5 Alpha. \\
        \textbf{Q2 2026} & \textbf{Hardware Matrix:} Certify \texttt{xInfer} on Intel NPU, Rockchip RK3588, and NVIDIA Jetson. \\
        \textbf{Q3 2026} & \textbf{Cloud Launch:} Launch managed SaaS version of Tower. \\
        \textbf{Q4 2026} & \textbf{Enterprise v1.0:} Full release with SOC2 Compliance, RBAC, and PDF Reporting. \\
        \bottomrule
    \end{tabular}
\end{table}

% ---------------------------------------------------------
% FINANCIALS
% ---------------------------------------------------------
\section{Financial Projections}

\begin{table}[h]
    \centering
    \begin{tabular}{@{}l c c c c@{}}
        \toprule
        \textbf{Metric} & \textbf{Year 1} & \textbf{Year 2} & \textbf{Year 3} & \textbf{Year 4} \\
        \midrule
        \textbf{Deployments} & 1,000 & 100,000 & 1M & 5M \\
        \textbf{ACV} & \$25k & \$40k & \$55k & \$70k \\
        \textbf{ARR} & \textbf{\$250k} & \textbf{\$2M} & \textbf{\$11M} & \textbf{\$42M} \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{Use of Funds (\$1.5M Pre-Seed)}
\begin{itemize}
    \item \textbf{45\% Engineering:} Hiring 2 Core C++ Engineers, 1 AI Researcher.
    \item \textbf{20\% Hardware Lab:} Purchasing Jetsons, FPGAs, and Industrial PLCs for testing.
    \item \textbf{20\% GTM \& Sales:} Developer Relations and Content Marketing.
    \item \textbf{15\% Operations:} Legal and Cloud Costs.
\end{itemize}

% ---------------------------------------------------------
% CONCLUSION
% ---------------------------------------------------------
\section{Conclusion}

Legacy SIEMs ask: \textit{``How much data can you send to our cloud?''} \\
\textbf{Blackbox} asks: \textit{``How much intelligence can we push to your device?''}

By breaking the hardware barrier with \texttt{xInfer}, Ignition AI is not just competing in the SIEM market; we are creating the \textbf{Ubiquitous AI Defense} category. We are building the engine that will secure the autonomous future.

\end{document}